Hydrodynamics of two vesicles interacting via a Van der Waals potential

### 2018-12-29 vesicle_code/docs/adhesion/adhesion.tex
revised figures added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Vesicles (self-enclosed phopholipid bilayer membranes) have been widely utilized
as simple model membranes for cell mimics in biomedical and material engineering \cite{}. 
%
The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
and electrohydrodynamics.
Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical (circular) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}. 
Various numerical schemes have been designed and deployed to simulate the hydrodynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}. In a vesicle suspension under 
a hydrodynamic flow or an external field (such as an electric field) 
the interactions between
vesicles play a crucial role in determining the collective dynamics of
vesicle suspension. For example, boundary integral simulations show that
vesicles may align to form chains along the external electric field,
enhancing the suspension viscosity in the direction of alignment.
In numerical simulations of vesicle suspension, it is often assumed that lubrication layer between vesicle membranes act to keep
membrane-membrane interaction (such as Van der Waals interaction) negligible \cite{BagchiJohoson2005_JBE,Veerapaneni2009_JCP}.

@@

\subsection{Effects of the adhesion parameters on equilibrium configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} 
In the simulations of a pair of 2d vesicles interacting with each other via the adhesion force in equation~\ref{eq:Fh} 
two vesicles are placed (not too far apart for numerical convenience) in a quiescent flow. Long-range attraction pulls two vesicles together as they deform until their
separation distance is close to $\delta$ (where $F$ vanishes). 
\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.25]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
\caption{Equilibrium shapes of wo vesicles under adhesive  interactions with adhesion strength $\sigma=0.5$ and separation distance $\delta=0.2$. 
Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$ as labeled.
 The color coding is the tension along the vesicle.}
\label{fig:Dec18_vesicle_shape}
\end{figure}

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_Eb_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_Eadh_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.125]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
\caption{Total bending energy (panel (a)), adhesion energy (panel (b)) and the sum of two energies (panel (c)) plotted against reduced area $\Delta A$.}
\label{fig:Dec18_vesicle_equilibrium1}
\end{figure}
Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending energy as a function of reduced area. The smaller the reduced area, the more vesicle area is available
for deformation and thus the bending energy is higher. Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b) shows the total adhesion energy as a function of reduced area. We note
that the total adhesion energy is more negative as reduced area decreases. The sum of two energies is plotted in figure~\ref{fig:Dec18_vesicle_equilibrium1}(c), where a local minimum in the total energy is
found around $\Delta A =0.8$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Vesicles (self-enclosed phopholipid bilayer membranes) have been widely utilized
as simple model membranes for cell mimics in biomedical and material engineering \cite{}. 
%
The ever expanding applications of vesicles have encouraged extensive investigations on vesicle hydrodynamics
and electrohydrodynamics.
Theoretical investigations are conducted to study the small-deformation or spheroidal dynamics of a nearly spherical  3D (or nearly circular 2D) vesicle in a fluid flow or under an external forcing \cite{Barthes-BieselRallison1981_JFM,Misbah2006_PRL,Vlahovska2007_PRE,Finken2008_EPL,ZhangZahnTanLin2013_PoF,Nganguia2013_PRE}. 
Various numerical schemes have been designed and deployed to simulate the hydrodynamics of many vesicles \cite{BagchiJohoson2005_JBE,Biben2005_EJP,Veerapaneni2009_JCP,SeolHuKimLai2016_JCP}.  
Experiments are performed to study vesicle hydrodynamics under various flowing conditions or forcing configurations \cite{MaderVitkova2006_EurPhysJE, Abkarian2008_SoftMatt,DahlNarsimhanGouveia2016_SoftMatt}. In a vesicle suspension under 
a hydrodynamic flow or an external field (such as an electric field) 
the interactions between
vesicles play a crucial role in determining the collective dynamics of
vesicle suspension. For example, boundary integral simulations show that
vesicles may align to form chains along the external electric field,
enhancing the suspension viscosity in the direction of alignment.
In numerical simulations of vesicle suspension, it is often assumed that lubrication layer between vesicle membranes act to keep
membrane-membrane interaction (such as Van der Waals interaction) negligible \cite{BagchiJohoson2005_JBE,Veerapaneni2009_JCP}.

@@

\subsection{Effects of the adhesion parameters on equilibrium configuration of a vesicle pair}
\label{subsec:qflow_adhesion_parameters} 
In the simulations of a pair of 2d vesicles interacting with each other via the adhesion force in equation~\ref{eq:Fh},
two vesicles are initially placed not too far apart  from each other for numerical convenience. 
Without any external forcing such as an imposed electric field or a fluid flow in the far-field, the long-range attraction pulls two vesicles together until their
separation distance is close to $\delta$ (where $F$ vanishes).  Depending on the adhesion strength relative to the membrane bending rigidity, the vesicle may deform significantly in the contact
region while still maintain nearly spherical shape on the opposite side to the contact region \cite{EvansMetcalfe1984_BJ,Book_PhysicalBasisCellAdhesion,Book_IntermolecularSurfaceForces,RamachandranAndersonLealIsraelachvili2010_Langmuir}.
\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
\caption{Two vesicles of length $\pi$ with $\kappa=1$, $\sigma=5$ and $\delta=0.2$.
(a) Equilibrium shapes of two vesicles under adhesive  interactions with adhesion strength $\sigma=0.5$ and separation distance $\delta=0.2$. 
Vesicle reduced area $\Delta A=0.95$, $0.75$ and $0.6$ as labeled.
 The color coding is the tension along the vesicle. (b) Membrane shapes in the contact region.}
\label{fig:Dec18_vesicle_shape}
\end{figure}

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
\caption{Two vesicles of length $\pi$ with $\kappa=1$, $\sigma=5$ and $\delta=0.2$. 
(a) Total bending energy (solid curve) and adhesion energy (dash-dotted curve) plotted against
the reduced area $\Delta A$. (b) Sum of two energies plotted against reduced area $\Delta A$.}
\label{fig:Dec18_vesicle_equilibrium1}
\end{figure}
Figure~\ref{fig:Dec18_vesicle_equilibrium1}(a) shows the total bending energy as a function of reduced area. The smaller the reduced area, the more vesicle area is available
for deformation and thus the bending energy is higher. Figure~\ref{fig:Dec18_vesicle_equilibrium1}(b) shows the total adhesion energy as a function of reduced area. We note
that the total adhesion energy is more negative as reduced area decreases. The sum of two energies is plotted in figure~\ref{fig:Dec18_vesicle_equilibrium1}(c), where a local minimum in the total energy is
found around $\Delta A =0.8$.
